Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-02 paper/paper.Rmd
Add text about ES & BF

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).

Next, following @etz2016, we compared Bayes Factors between the original and replication. While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates. This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).

This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well. Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g. BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.

>>>>

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom. Other formulas are given in @osc2015, supplemental]. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).

While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates. This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default  test suggested by @rouder2009 and did not attempt to correct for publication bias. This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well. Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g. BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.
